\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[margin=1in]{geometry}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Peter Cunha}}\\
	Los Angeles, CA $\cdot$ peter@alumni.purdue.edu $\cdot$ (310) 818-1425\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Purdue University}\hfill West Lafayette, IN\\
BS Computer Science \textit{GPA: 3.2} \hfill 2016 - 2020\\
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Northrop Grumman} \hfill Space Park, CA\\
\textit{Software Engineer} \hfill 2015 | 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Worked on the Kestrel Ground Systems team to built a fully featured web dashboard for visualizing live mission data. Live satellite telemetry graphs, command \& control capabilities, and an authentication \& user management system. Node.js, MongoDB, D3.js, Angular. (2019)
	\item Improved on satellite ground system software by adding load balancing, service discovery, and fault tolerance in C++. Built a Web UI for monitoring and controlling satellite ground systems using Node.js and Angular. (2018)
	\item Worked with a team of talented developers to build a satellite ground system in C++ and Java. Capabilities included decoding RF signals from long-range antennas, translating binary streams into meaningful data, and distributing that data to many systems using ActiveMQ. (2017)
	\item Developed and maintained an HR software tool for managing incoming and existing employees. Added features, fixed bugs, and wrote documentation. PHP, MySQL, JavaScript. (2016)
\end{itemize}
\textbf{BitMitigate} \hfill Los Angeles, CA\\
\textit{Network Security Engineer} \hfill 2014 | 2015\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Built network stress testing tools to simulate real world DDoS attacks. We used this technology to help companies prepare for large-scale cyber threats..
\end{itemize}
\textbf{Wintermute Technology} \hfill Torrance, CA\\
\textit{Software Engineer (Remote)} \hfill 2014 | Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Created custom software solutions for our customers. These solutions included cybersecurity tools, fully-featured websites, cloud applications, and custom automation tools. Primarily used MySQL, Java, Go (for backend software) or Node.js, React, and MongoDB (web development).
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages: & Java, C++, Javascript, Go, Python, Angular, React, Node.js, PHP, CSS \\
	Technologies:          & Docker, Apache, Nginx, Jenkins, MySQL, MongoDB, Elasticsearch        \\
	Cloud:                 & Amazon Web Services, Google Cloud Platform, Digital Ocean            \\
	Other:                 & Agile, CI/CD, Design Patterns, Git                                   \\
\end{tabular}
\vspace{2mm}

\header{Links}
{\textbf{Github}}\hfill https://github.com/petercunha\\
My open source projects\\
\vspace*{2mm}
{\textbf{Leetcode}}\hfill https://leetcode.com/sunlit\\
My competetive programming profile\\
\vspace*{2mm}
{\textbf{Personal Website}}\hfill https://petercunha.com\\
My personal website with more info about me\\
\vspace*{2mm}

\header{Achievements}
\textbf{Cyberpatriot National Finalist} \hfill U.S. Air Force\\
Team ranked 6th place in the nation for Cyberpatriot, a national cyber defense competition.\\
\vspace*{2mm}
\textbf{Amazon.com Security Researcher} \hfill Amazon.com, Inc.\\
Discovered a serious vulnerability in Amazon.com\textquotesingle{}s web interface, allowing for the account theft of anyone who clicked on a malicious link.\\
\vspace*{2mm}
\textbf{Cryptography Certification} \hfill Stanford University\\
Completed Stanford University\textquotesingle{}s online Cryptography program through Coursera.\\
\vspace*{2mm}

\ 
\end{document}